---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = 'tests/testthat/')
```

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.path = "README-")
```

```{r echo=FALSE, message=FALSE}
install.packages("../..", repos = NULL, type = "source")
```

# subtitler

[![Build Status](https://travis-ci.org/benjcunningham/subtitler.svg?branch=master)](https://travis-ci.org/benjcunningham/subtitler)
[![Coverage Status](https://img.shields.io/coveralls/benjcunningham/subtitler.svg)](https://coveralls.io/github/benjcunningham/subtitler?branch=master)

Read and write video subtitle formats.


## Install

```{r eval=FALSE}
devtools::install_github("benjcunningham/subtitler")
```

## Quick Demos

```{r message=FALSE}
library(subtitler)
library(tidyverse)
library(tidytext)
library(stringr)
```

### Adjusting Timestamps

```{r echo=FALSE, comment=NULL}
read_file("Always_Sunny_S10E04.srt") %>%
  cat()
```

Consider the above SubRip file and suppose we have observed that every subtitle lags by half a second. Using the `add_milliseconds()` function, we can easily adjust the timestamp of every block accordingly. We can even write back to file in the original format using `write_srt()`.

```{r sunny-demo}
f <- tempfile()

read_srt("Always_Sunny_S10E04.srt") %>%
  mutate(
    start = add_milliseconds(start, -500),
    end   = add_milliseconds(end,   -500)
  ) %>%
  write_srt(f)
```

### Text Mining

The package may also be useful for getting subtitles into a tidytext workflow. For example, [I previously reproduced](http://benjcunningham.org/2017/03/05/introducing-subtitler-0-1-0.html) part of [this article by Oliver Roeder of FiveThirtyEight](https://fivethirtyeight.com/features/complete-catalog-curses-deaths-quentin-tarantino-films/), cataloging all of the times someone swore in one of Quentin Tarantino's movies. The script below mirrors the analysis on subtitles from _The Wolf of Wall Street_.

```{r wolf-demo, fig.width=10, fig.height=2}
df <- read_srt("The_Wolf_of_Wall_Street.srt")

df %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "[fs](uc|hi)[kt]")) %>%
  mutate(min = floor(as_milliseconds(start) / 6e4)) %>%
  ggplot(aes(min)) +
    geom_bar() +
    labs(x = "Minute", y = "# of Curses", title = "The Wolf of Wall Street (2013)") +
    scale_x_continuous(breaks = seq(0, 180, 60), limits = c(0, 180))
```

## License

MIT &copy; Ben Cunningham
